% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
\usepackage{amsmath}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

\begin{document}

\name{Tomas McCandless}
% \address used twice to have two lines of address
\address{\textbf{email:} tomas.mccandless@gmail.com, \textbf{phone:} (210) 232-1477} 
\address{\textbf{web:} tomasmccandless.com}

 
\begin{resume}
 
 
\section{EDUCATION} {\sl Master of Science,} Computer Science \\
                    {\sl Bachelor of Science,} Computer Science \\
										{\sl Bachelor of Arts,} Philosophy \\
                % \sl will be bold italic in New Century Schoolbook (or
	        % any postscript font) and just slanted in
		% Computer Modern (default) font
                University of Texas at Austin 
                (expected May 2014) \\
								GPA: 3.67  $\;$ CS GPA: 3.73 
 
\section{TECHNICAL \\ SKILLS} {\sl Fluent:} Java, Matlab, C, Python, Linux/Unix, git \\
                {\sl Familiar:} C++, Ruby, LISP, Haskell, Prolog, \LaTeX, HBase, gwt, JavaCC, libsvm \\


                              \section{SELECTED PUBLICATIONS} {\sl Object-Centric Spatio-Temporal Pyramids for Egocentric Activity Recognition}
	\begin{itemize} \itemsep -2pt
  \item To appear, British Machine Vision Conference, 2013
	\item Multi-resolution histograms of detected objects used as feature vectors
	\item Boosting and SVMs for classification of first-person video
	\end{itemize}


\section{RESEARCH} {\sl Linear vs. Hierarchical Segmentation of Egocentric Video} 
	\begin{itemize} \itemsep -2pt
	\item Partition hours of first-person video into events 
	\item k-means clustering with temporal constraints (tck-means)
	\item Histogram intersection using pixel intensities as features
	\item Prototype UI for fast video browsing based on linear or hierarchical segmentation
	\end{itemize}

\section{EXPERIENCE} {\sl Software Engineering Intern} \hfill Summers 2012-2013 \\
                Workday, 
                Performance Engineering, Pleasanton, CA
                 \begin{itemize}  \itemsep -2pt % reduce space between items
                 \item Researched and deployed a distributed, scalable system for collecting and visualizing performance metrics.
								 \item Over 500 different metrics collected from MySQL, Linux kernel, etc.
                 \item Developed a webapp using gwt for downloading collected data.
                \end{itemize}

                {\sl Research Assistant } \hfill Spring 2013 \\
                Computational Visualization Center, University of Texas at Austin
                \begin{itemize} \itemsep -2pt
                    \item TexMol, a software package used for computational drug discovery.
                    \item Developed a method for scoring strength of molecular bonds.
                    \item UI design and implementation using qt4.
                 \end{itemize}
        
 
                {\sl Undergraduate Assistant} \hfill        2010-2011 \\
                Department of Computer Science, University of Texas at Austin
                  \begin{itemize} \itemsep -2pt
                   \item Graded exams, assisted students in Algorithms and Data Structures with designing and debugging Java programs.
                   \end{itemize} 
 
\section{SELECTED COURSEWORK} {\sl Graduate:} \\ Parallel Algorithms, Machine Learning, Programming Languages, Formal Semantics \\
															{\sl Undergraduate:} \\ Computer Vision, Information Retrieval, Operating Systems, Algorithms, 
															Artificial Intelligence, Computer Graphics, Computational Linguistics, Programming for Correctness, 
															Probability, Number Theory \\

                           
\iffalse
\section{EXTRA-CURRICULAR \\ ACTIVITIES}            
								{\sl Recipient,} Chevron Scholarship (2012) \\
								{\sl Recipient,} Tracor/Frank McBee, Jr. Scholarship (2011) \\
                Association for Computing Machinery \\
								Undergraduate Philosophy Association \\
								Longhorn Billiards Club
                \fi
\end{resume}
\end{document}







